---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.  -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Coral R data package

<!-- badges: start -->
<!-- badges: end -->

The goal of the coral package is to provide data on the species and characteristics of corals around the globe. This dataset is managed by the Coral Trait Database, and serves as a regulated repository for survey data collected on corals by many different research groups and projects. 

## Installation

The development version of 0.1.0 is available from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Reed-Math241/pkgGrph")
```
## Example

###Load Package
```{r example}
library(pkgGrph)
```




